\TheTitle

### 2017-07-15 paper/discussion.tex
adding fixes for discussion

The results show conclusive results; the DAG visualization is unable to
adequately provide users with an explanation of the changes being made
in the repository, the DAG visualizatoin is not easily understood, and
is unable to provide summarizations of the changes being made at a
merge. Meanwhile, the \mt visualization is better able to provide an
explanation of how a commit is integrated, along with better
summarization. In this section, we discuss some observations, threats to
the validity, and comments made by the participants during the study
followed by discussion about modifications to the original algorithm to
help generalize it for more repositories, concluded with future work.

@@

% \dmg{I think you mean challenge using gitk, right? so be explicit}

During the course of the study, we noticed an issue that was consistent
among the participants when using Gitk; the most difficult challenge was
identifying the master branch of the repository. Many participants would
identify the tag as being the ``master branch'', but a tag is not a
branch. The visualization of the DAG does not provide any notion of
which branch being shown is the master branch. The default assumption is
that the first branch on the left is the master branch, but this is not
a good assumption. Furthermore, the visualization in Gitk is not
consistent, the ordering of the branches changes between runs, so
identifying the branch once will not guarantee that it will be
identifiable after restarting Gitk.

If users were able to easily identify the master branch using the
visualizations of the DAG, the results of the study would likely be very
different. This would certainly be the case for the single-commit tree;
it is trivial to summarize information about a single item, but
identifying that there was only a single commit in the tree was
non-trivial. This information is important because many trees contain a
single commit, and the structure of these trees is identical to the
structure of flat trees. Flat trees are the most common branching
structure in the repository, with the root being the parent to all of
the other nodes in the tree; to improve summarization and comprehension
of these trees, it would likely by sufficient to indicate the master
branch in the DAG visualization.

@@

One participant in the study worked as a release manager for more than
three years, working with both SVN and CVS repositories, but had little
experience with git. This subsection contains improvements made by this
participant during the study and afterward.

Contributors making merges need to understand more than just what merges
a commit was collected into before reaching the repository of the
contributor. It is also important to understand order that the related
commits were made, as the order tells the story of what the developer
was thinking as they were writing the changes. The current \mt model
does not order the commits, simply placing them randomly. This is the
primary reason behind this participant's request to use both
simultaneously. \tool is able to help with the aggregation of the
information, and provide a better understanding of the next merge
involved in integrating this commit, but the DAG visualization in Gitk
provides the full story of the commit instead of hiding it behind a
layer of abstraction.

@@

The answers provided by the participants to earlier tasks were not
taken into account for determining the accuracy. If the participant was
unable to determine the correct commits for the tree within the
conceptual task group, the summarization results would be recorded as
wrong, even if the summarization they provided was correct for the set
of commits selected to be part of the tree. A further study could be
done where the correct answer was provided to the participant after each
task so that errors would not propagate between tasks.

@@

% A possible
% reason for this may be that unless a repository reaches a sufficient
% complexity, both in branching and number of commits, these tools are
% unnecessary for the normal operation of git. Furthermore, fear of the
% complexity caused by branching may cause personal and academic
% repositories to have relatively simple structures. While they were
% unfamiliar with the DAG structure, these users were also unfamiliar with
% the \mt model, and were still able to better understand and summarize
% the repository using \tool.

\subsection{Generalization}
\label{sub:generalization}

@@

If this algorithm is to be generalized into a dynamic, web-based, tool,
it may not be feasible to download every every repository event in the
repository in a reasonable period of time. We instead look toward a
breadth-first approach at limiting the number of repository events that
must be downloaded.

>>>>

\section{Discussion}
\label{sec:discussion}

The results show conclusive results; the DAG visualization provided by
Gitk is unable to provide an explanation of the changed being made in
the repository, is not easily understood, and is unable to provide
summarizations of the changes being made at a merge. Meanwhile, the \mt
visualization of \tool is better able to provide an explanation of how a
commit is integrated, along with better summarization. In this section,
we discuss some observations, threats to the validity, and comments made
by the participants during the study followed by discussion about
modifications to the original algorithm to help generalize it for more
repositories, concluded with future work.

@@

During the course of the study, we noticed an issue that was consistent
among the participants when using Gitk; the most difficult challenge was
identifying the master branch of the repository. Many participants would
identify the tag as being the ``master branch'', but a tag is not a
branch (it simply points to a given commit). The visualization of the DAG does not provide any notion of
which branch being shown is the master branch. The default assumption is
that the first branch on the left is the master branch, but this is not
always correct. Furthermore, the visualization in Gitk is not
consistent, the ordering of the branches changes between runs, so
identifying the branch once will not guarantee that it will be
identifiable after restarting Gitk.

% \evan{I watch the DAG change three times in a row on the visualization for \comB}

If users were able to easily identify the master branch using the
visualizations of the DAG, the results of the study would likely be very
different, making the differences between Gitk and \tool less
significant. This would help in the case of the single-commit trees, it
is trivial to summarize information about a single item, but identifying
that there was only a single commit in the tree was non-trivial. This
information is important because more than a quarter of the trees in the
Linux repository contain a single commit, and the structure of these
trees is identical to the structure of flat trees. Flat trees are the
most common branching structure in the repository, with the root being
the parent to all of the other nodes in the tree; to improve
summarization and comprehension of these trees, it would likely by
sufficient to indicate the master branch in the DAG visualization.

@@

One participant in the study worked as a release manager for more than
three years, working with both SVN and CVS repositories, but had little
experience with git. This subsection contains improvements proposed by
this participant during the study and afterward.

Contributors making merges need to understand more than just what merges
a commit was collected into before reaching the repository of the
contributor. It is also important to understand order that the related
commits were made, as the order tells the story of what the developer
was thinking as they were writing the changes. The visualization of the
\mt in \tool does not order the commits, randomly ordering them in each
level. The \mt model does retain this information, so implementing this
modification is trivial. This is the primary reason behind this
participant's request to use both tools simultaneously. \tool is able to
help with the aggregation of the information, and provide a better
understanding of the next merge involved in integrating this commit, but
the DAG visualization in Gitk provides the full story of the commit
instead of hiding it behind a layer of abstraction.

@@

The answers provided by the participants to earlier tasks were not taken
into account for determining correctness or accuracy in further
questions. An incorrect answer may impact the results of the tasks that
followed. If the participant was unable to determine the correct commits
for the tree within the conceptual task group, the summarization results
would be recorded as wrong, even if the summarization they provided was
correct for the set of commits selected to be part of the tree. A
further study could be done where the correct answer was provided to the
participant after each task so that errors would not propagate between
tasks.

@@

The participants in the study were students, some with industrial
experience. Most of the participants had worked relatively few
collaborators, so professional developers may have been able to better
comprehend the DAG visualizations in Gitk.

\section{Generalizing the Creation of the \mt}
\label{sub:generalization}

@@

If this algorithm is to be generalized to work in a dynamic, web-based,
tool it may not be feasible to download every every repository event in the
repository in a reasonable period of time. We instead look toward a
breadth-first approach at limiting the number of repository events that
must be downloaded.
